The \dealii Library, Version 9.6

### 2024-08-12 9.6/paper.tex

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Bruno Blais,
    Marc Fehling,
    Rene Gassm"{o}ller,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Matthias Maier,
    Peter Munch,
    Bruno Turcksin,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.6, 2024},
}

@@

\author[12]{Bruno~Turcksin}

\author[13]{David Wells}
\affil[13]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

@@

% This is up-to-date as of 2024-07-23 11:52PM CEST
\begin{quote}
Laryssa      Abdala,
Pasquale     Africa,
Mathias      Anselmann,
Abbas        Ballout,
Maximilian   Bergbauer,
Julian       Brotz,
Marco        Feder,
Niklas       Fehn,
Menno        Fraters,
Quang        Hoang,
Vladimir     Ivannikov,
Tao          Jin,
Yimin        Jin,
Sebastian    Kinnewig,
Paras        Kumar,
Sébastien    Loriot,
Nils         Much,
Abdullah     Mujahid,
Bob          Myhill,
Paul A.      Patience,
Luz          Paz,
Laura        Prieto Saavedra,
Sebastian    Proell,
Hendrik      Ranocha,
Johannes     Resch,
Andreas      Ritthaler,
Malik        Scheifinger,
David        Schneider,
Magdalena    Schreter,
Richard      Schussnig,
Nils         Schween,
Kyle         Schwiebert,
Simranjeet   Singh,
Simon        Sticko,
Dominik      Still,
Jan Philipp  Thiele,
Thierry      Thomas,
Vinayak      Vijay,
Ivy          Weber,
Simon        Wiesheier,
Chengjiang   Yin,
Vladimir     Yushutin,
Stefano      Zampini.
\end{quote}
Their contributions are much appreciated!

>>>>

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Bruno Blais,
    Marc Fehling,
    Rene Gassm"{o}ller,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Matthias Maier,
    Peter Munch,
    Magdalena Schreter-Fleischhacker,
    Jan Philipp Thiele,
    Bruno Turcksin,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.6, 2024},
}

@@

\author[12]{Magdalena Schreter-Fleischhacker}
 \affil[12]{Institute for Computational Mechanics, Technical University of Munich, Boltzmannstraße 15, 85748 Garching, Germany.
  {\texttt{magdalena.schreter@tum.de}}}

\author[13]{Jan Philipp Thiele}
 \affil[13]{Weierstrass Institute for Applied Analysis and Stochastics,\newline
 Leibniz Institute in Forschungsverbund Berlin e.V.
  {\texttt{thiele@wias-berlin.de}}}

\author[14]{Bruno~Turcksin}

\author[15]{David Wells}
\affil[15]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

@@

% This is up-to-date as of 2024-07-23 11:52PM CEST
\begin{quote}
Laryssa      Abdala,
Pasquale     Africa,
Mathias      Anselmann,
Abbas        Ballout,
Maximilian   Bergbauer,
Julian       Brotz,
Marco        Feder,
Niklas       Fehn,
Menno        Fraters,
Quang        Hoang,
Vladimir     Ivannikov,
Tao          Jin,
Yimin        Jin,
Sebastian    Kinnewig,
Paras        Kumar,
Sébastien    Loriot,
Nils         Much,
Abdullah     Mujahid,
Bob          Myhill,
Paul A.      Patience,
Luz          Paz,
Laura        Prieto Saavedra,
Sebastian    Proell,
Hendrik      Ranocha,
Johannes     Resch,
Andreas      Ritthaler,
Malik        Scheifinger,
David        Schneider,
Magdalena    Schreter-Fleischhacker,
Richard      Schussnig,
Nils         Schween,
Kyle         Schwiebert,
Simranjeet   Singh,
Simon        Sticko,
Dominik      Still,
Jan Philipp  Thiele,
Thierry      Thomas,
Vinayak      Vijay,
Ivy          Weber,
Simon        Wiesheier,
Chengjiang   Yin,
Vladimir     Yushutin,
Stefano      Zampini.
\end{quote}
Their contributions are much appreciated!
